---
title: "Alcohol vs Seat choice"
author: "Jiselle Barba"
date: "Fall 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```
  
Visually, the plot show a substantial amount of a difference between the back row and the middle row and an even bigger difference between the back row and the front row.  
  
## Numerical Summarys 
  
```{r}
favstats(alcohol~Seat,data=davisdata)
```
  According to the chart, the back row drinks 9.6 more alcoholic drinks than the middle row, drinking only about 3.2 alcoholic drinks per week. The front row drinks 1.8 per week. It is reasonable to assume that the amount being drank per week is not the same between these 3 rows.
    
## Inferential Tests
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
The P value represents the chances of obtaining the result we just got if the null hypothesis is actually true. Since the result is so small, I am going to reject the null hypothesis.  
We now need to look to see if we can discover what is different from the other.
     
```{r}
plot(TukeyHSD(model1))
```
  
According to this chart, the middle and front do not have a difference. However, the front-back and the back-middle are different.  
  
## Conclusions
  
  In conclusion, we found out that there were three different categories instead of two. We had to use Anova to determine the amount of drinks per week by the rows the people sat in.
The back row drinks 9.6 more alcoholic drinks than the middle row, drinking only about 3.2 alcoholic drinks per week. The front row drinks 1.8 per week. It is reasonable to assume that the amount being drank per week is not the same between these 3 rows. The P value represents the chances of obtaining the result we just got if the null hypothesis is actually true. Since the result is so small, I am going to reject the null hypothesis. The middle and front rows do not have a difference. However, the front-back and the back-middle are different. 

