---
title: "Alcohol vs Seat choice"
author: "Jiselle Barba"
date: "Fall 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys 
  
```{r}
favstats(alcohol~Seat,data=davisdata)
```
  According to the chart, the back row drinks the most alcohol than the middle and front rows. The back row drinks a mean of 9.625000. The middle row drinks a mean of 3.283133. The front row drinks a mean of 1.803030.  
    
## Inferential Tests

## Conclusions


